Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-03-01 siip.tex
siip draft, so messy

\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
\usepackage{fancyhdr}
\usepackage{pagecounting}
\usepackage[dvips]{color}
\usepackage{graphicx}

@@

          The goal will be to explore whether curriculum development can 
          operate like open source software development does, drawing on a 
          community of experts toward creating a shared core resource. In open 
          source software, developers share code revisions in online 
          repositories. In a typical project, the main 'fork' holds the 
          official copy of the software package. Developers each have their own 
          forks, copies of the repository, where they are able to make changes 
          on their own.

          This initiative already involves a 
          few peer professors -- faculty in Nuclear Engineering from UC 
          Berkeley, U. Wisconsin at Madison, Kansas State, U. South Carolina, 
          and U. Tennessee-Knoxville. We all use GitHub \cite{github} to store, 
          revise, and collaborate on research, especially source code. A few 
          of us have already started to host our course curricula online as 
          well, but these are typically single author repositories \cite{}.

          The participants will collaborate on a master set of learning 
          modules} for a common upper-division course in nuclear engineering : 
          The Nuclear Fuel Cycle.  The curriculum will be hosted on GitHub, 
          used by all of us, and improved continually as we learn and grow as 
          instructors.

@@

          \end{document}

>>>>

\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries
\usepackage{fancyhdr}
\usepackage{pagecounting}
\usepackage[dvips]{color}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}

@@

          The goal will be to explore whether curriculum development can 
          operate like open source software development does, drawing on a 
          community of experts toward creating a shared core resource. In open 
          source software, developers share code revisions in online 
          repositories. In a typical project, the main ``fork'' holds the 
          official copy of the software package. Developers each have their own 
          forks, copies of the repository, where they can work on features and 
          bug fixes. When those features and bug fixes are ready for prime 
          time, the developer makes a ``pull request'' to the main fork, it is 
          reviewed by their collaborators, and it is eventually merged into the 
          main fork where it can be used by all.

          \begin{figure}
                  \centering
                  \begin{subfigure}{.4\textwidth}
                            \centering
                              \includegraphics[width=.8\linewidth]{git-flow}
        \caption{This figure, from \cite{scopatz_effective_2016}, captures a process, often called Git Flow, through which a new feature or bug fix enters a piece of open source software \cite{scopatz_effective_2016}.}
                                  \label{fig:sub1}
                  \end{subfigure}\hfill%
                  \begin{subfigure}{.4\textwidth}
                            \centering
                              \includegraphics[width=.8\linewidth]{siip-flow}
  \caption{This adaptation imagines the process in the context of learning module development, using the same git version control system and GitHub repository hosting framework.}
                                  \label{fig:sub2}
                  \end{subfigure}
                  \caption{A figure with two subfigures}
                  \label{fig:test}
          \end{figure}

          This initiative already involves a few peer professors. Six faculty 
          in Nuclear Engineering from UC Berkeley, the University of Wisconsin 
          at Madison, Kansas State, U. South Carolina, and U. 
          Tennessee-Knoxville are involved. We all use GitHub \cite{github} to 
          store, revise, and collaborate on research, especially source code. A 
          few of us have already started to host our course curricula online as 
          well, but these are typically single author repositories 
          \cite{skutnik,wilson,slaybaugh,scopatz,borelli,roberts}.

          The participants will collaborate on a master set of learning 
          modules for an upper-division course in nuclear engineering : 
          The Nuclear Fuel Cycle.  The curriculum will be hosted on GitHub, 
          used by all of us, and improved continually as we learn and grow as 
          instructors.

@@

          \section{Departmental Support}
          The Department of Nuclear, Plasma, and Radiological Engineering will 
          support this work with relese time through startup funds. 
          Additionally, NPRE will support workshop activities through 
          administrative effort and by providing space.
          \end{document}
